\textsc{PAPERCLIP}: Associating Astronomical Observations and Natural Language with Multi-Modal Models

### 2024-03-11 paper/hubble_paperclip.tex
Reference to overview figure
Spheres in paper

In this paper, we describe \text{PAPERCLIP} (Proposal Abstracts Provide an Effective Representation for Contrastive Language-Image Pre-training\footnote{Technically, we fine tune rather than pre train, but ``PAPERCLIFT'' was rejected by the senior author of this paper.}), a method that connects astronomical image observations with natural language by leveraging the association between abstracts of successful observing proposals and images corresponding to downstream observations. 
%
Concretely, we showcase the method using observations imaged by the \hubble Space Telescope (HST).
%
We show that fine-tuning a pre-trained CLIP ~\citep[Contrastive Language-Image Pre-training; ][]{radford2021learning} image-text model on observation-abstract pairs results in meaningful joint representations through quantitative and qualitative evaluation tests.
%
Our method opens up the possibility of interacting with astronomical survey data using free-form natural language as an interface, which is a cornerstone of the success of the modern foundation model paradigm.
%

@@

\section{\changes{Related work}}

@@

The guided generation process ensures that, in this case, the output of the LLM strictly conforms to the format of the following example:
\begin{center}
  \begin{jsoncode}
    \centering
          \color{black}\{
            \color{codegreen}'objects_and_phenomena'\color{black}: [\color{codegreen}'star forming galaxy', 'lensed galaxy'\color{black}], 
            \color{codegreen}'science_use_cases'\color{black}: [\color{codegreen}'measure lensing magnification'\color{black}]
          \color{black}\}
  \end{jsoncode}
  \end{center}
which is then used to construct the summarized caption by combining the two key elements.
%
Examples of raw abstract snippets and corresponding LLM-generated summaries are shown in Tab.~\ref{tab:datasetsumm}.
%
We train separate models using the raw abstracts and the LLM-generated summaries, and compare their performance on downstream tasks in Sec.~\ref{sec:results}.
%
We note that, even after summarization, the association signal is expected to be noisy, since parts of the summarized caption may not be directly descriptive of the observed images. The goal of the fine-tuning process is to leverage the signal contained in this noisy association.

>>>>

In this paper, we describe \text{PAPERCLIP} (Proposal Abstracts Provide an Effective Representation for Contrastive Language-Image Pre-training\footnote{Technically, we fine tune rather than pre train, but ``PAPERCLIFT'' was rejected by the senior author of this paper.}), a method that connects astronomical image observations with natural language by leveraging the association between abstracts of successful observing proposals and images corresponding to downstream observations. 
%
Concretely, we showcase the method using observations imaged by the \hubble Space Telescope (HST).
%
We show that fine-tuning a pre-trained CLIP ~\citep[Contrastive Language-Image Pre-training; ][]{radford2021learning} image-text model on observation-abstract pairs results in meaningful joint representations through quantitative and qualitative evaluation tests.
%
Our method opens up the possibility of interacting with astronomical survey data using free-form natural language as an interface, which is a cornerstone of the success of the modern foundation model paradigm. \changes{A high-level overview of the method is shown in Fig.~\ref{fig:overview}}.
%

@@

\section{\changes{Related Work}}

@@

The guided generation process ensures that, in this case, the output of the LLM strictly conforms to the format of the following example:
\begin{center}
  \begin{jsoncode}
    \centering
          \color{black}\{
            \color{codegreen}'objects_and_phenomena'\color{black}: [\color{codegreen}'star forming galaxy', 'lensed galaxy'\color{black}, ...], 
            \color{codegreen}'science_use_cases'\color{black}: [\color{codegreen}'measure lensing magnification'\color{black}, ...]
          \color{black}\}
  \end{jsoncode}
  \end{center}
which is then used to construct the summarized caption by combining the two key elements.
%
Examples of raw abstract snippets and corresponding LLM-generated summaries are shown in Tab.~\ref{tab:datasetsumm}.
%
We train separate models using the raw abstracts and the LLM-generated summaries, and compare their performance on downstream tasks in Sec.~\ref{sec:results}.
%
We note that, even after summarization, the association signal is expected to be noisy, since parts of the summarized caption may not be directly descriptive of the observed images. The goal of the fine-tuning process is to leverage the signal contained in this noisy association.
